\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-30 paper.tex
Fix the issue not appearing space after p-D and k-D
Changed font size of the notation table
Changed the notation order

\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-1in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.7in}%
\addtolength{\topmargin}{-1in}%
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\def\tightlist{}
\usepackage{setspace}
\newcommand\pD{$p\text{-}D$}
\newcommand\kD{$k\text{-}D$}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{agsm}
\usepackage{bookmark}

@@

\caption{\label{tab:tbl-notations}Notations used in this paper.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n$ & number of observations\\
$p$ & number of dimensions in $p$-D data\\
$X_{n \times p} = \begin{bmatrix} \textbf{x} _{1} & \textbf{x}_ {2} & \cdots & \textbf{x}_{n} \\  \end{bmatrix}^\top$ & $p$-D data matrix\\
$d$ & number of dimensions in embedding data, usually two\\
$Y_{n \times d} = \begin{bmatrix} \textbf{y} _{1} & \textbf{y}_ {2} & \cdots & \textbf{y}_{n} \\  \end{bmatrix}^\top$ & embedding matrix\\
\addlinespace
$P_t$, $P_{t+1}$ & point along the geodesic path at time $t$ and the next time instant, which is $t+1$\\
$y_max$ & maximum value of the scaled second embedding component\\
$r_1$, $r_2$ & range of the first and  second embedding component\\
$h_b$, $w_b$ & height and width of the hexagon\\
$a_r$ & aspect ratio of the 2D layout before scaling\\
\addlinespace
$h_r$ & hexagon ratio\\
$s$ & hexagonal size (radius of the outer circle surrounding the hexagon)\\
$(x_s, y_s)$ & starting coordinates of the hexagonal grid\\
$q_x$, $q_y$ & buffer amount along the x and y axes\\
$h_s$, $v_s$ & horizontal and vertical distance between adjacent hexagon bin centroids\\
\addlinespace
$d_x$ & horizontal spacing\\
$d_y$ & adjusted vertical spacing for hexagonal coordinates\\
$b_x$, $b_y$ & number of hexagon bins along the x and y axes\\
$b$ & total number of hexagon bins in the grid\\
$b'$ & number of hexagon bins without the empty bins\\
\addlinespace
$n_k$ & number of observations within $k^{th}$ hexagon\\
$(h^k_{x_i}, h^k_{y_i})$ & hexagonal grid coordinates of $k^{th}$ hexagon\\
$C_k^{(2)} \equiv (C_{ky_1}, C_{ky_2})$ & hexagonal bin centroid coordinates of $k^{th}$ hexagon\\
$C_k^{(p)} \equiv (C_{kx_1}, ..., C_{kx_p})$ & $p$-D mappings of 2D hexagonal bin centroids of $k^{th}$ hexagon\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-1in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.7in}%
\addtolength{\topmargin}{-1in}%
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\def\tightlist{}
\usepackage{setspace}
\newcommand\pD{$p\text{-}D$\ }
\newcommand\kD{$k\text{-}D$\ }
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{agsm}
\usepackage{bookmark}

@@

\caption{\label{tab:tbl-notations}Notations used in this paper.}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n$ & number of observations\\
$p$ & number of dimensions in $p$-D data\\
$d$ & number of dimensions in embedding data, usually two\\
$X_{n \times p} = \begin{bmatrix} \textbf{x} _{1} & \textbf{x}_ {2} & \cdots & \textbf{x}_{n} \\  \end{bmatrix}^\top$ & $p$-D data matrix\\
$Y_{n \times d} = \begin{bmatrix} \textbf{y} _{1} & \textbf{y}_ {2} & \cdots & \textbf{y}_{n} \\  \end{bmatrix}^\top$ & embedding matrix\\
\addlinespace
$P_t$, $P_{t+1}$ & point along the geodesic path at time $t$ and the next time instant, which is $t+1$\\
$y_max$ & maximum value of the scaled second embedding component\\
$r_1$, $r_2$ & range of the first and  second embedding component\\
$h_b$, $w_b$ & height and width of the hexagon\\
$a_r$ & aspect ratio of the 2D layout before scaling\\
\addlinespace
$h_r$ & hexagon ratio\\
$s$ & hexagonal size (radius of the outer circle surrounding the hexagon)\\
$(x_s, y_s)$ & starting coordinates of the hexagonal grid\\
$q_x$, $q_y$ & buffer amount along the x and y axes\\
$h_s$, $v_s$ & horizontal and vertical distance between adjacent hexagon bin centroids\\
\addlinespace
$d_x$ & horizontal spacing\\
$d_y$ & adjusted vertical spacing for hexagonal coordinates\\
$b_x$, $b_y$ & number of hexagon bins along the x and y axes\\
$b$ & total number of hexagon bins in the grid\\
$b'$ & number of hexagon bins without the empty bins\\
\addlinespace
$n_k$ & number of observations within $k^{th}$ hexagon\\
$(h^k_{x_i}, h^k_{y_i})$ & hexagonal grid coordinates of $k^{th}$ hexagon\\
$C_k^{(2)} \equiv (C_{ky_1}, C_{ky_2})$ & hexagonal bin centroid coordinates of $k^{th}$ hexagon\\
$C_k^{(p)} \equiv (C_{kx_1}, ..., C_{kx_p})$ & $p$-D mappings of 2D hexagonal bin centroids of $k^{th}$ hexagon\\
\bottomrule
\end{tabular}
\end{table}
